Wigglyhedra

### 2024-06-12 draft/wigglyhedra.tex
Kept second version of remark + cleaning.

\begin{remark}\label{rem:generating-morphisms}
  It is easy to check that the generating objects \(P_i\) (and hence their graded and homological shifts) satisfy the following:
  \begin{itemize}
  \item \(\Hom^{g,h}(P_i,P_i) = 0\) if \(g \neq 0, 2\) and \(h \neq 0\),
  \item \(\Hom^{g,0}(P_i,P_i) = k\) if \(g = 0, 2\),
  \item \(\Hom^{g,h}(P_i, P_{i\pm1}) = 0\) if \(g \neq 1\) and \(h \neq 0\),
  \item \(\Hom^{1,0}(P_i, P_{i\pm1}) = k\), and
  \item \(\Hom^{g,h}(P_i, P_j) = 0 \) otherwise.
  \end{itemize}
\end{remark}

\vincent{What about this remark instead?}
\begin{remark}\label{rem:generating-morphisms}
  It is easy to check that the generating objects \(P_i\) (and hence their graded and homological shifts) satisfy \(\Hom^{0,0}(P_i,P_i) = \Hom^{1,0}(P_i,P_i) = \Hom^{1,0}(P_i,P_{i\pm1}) = k\) and \(\Hom^{g,h}(P_i, P_j) = 0\) in all other cases.
\end{remark}

@@

We refer the reader to e.g.~\cite[Sect.~1.3]{bel.ber.del:82} for the definition of a \(t\)-structure on a triangulated category.
The following proposition is easily checked using the calculations in~\cref{rem:generating-morphisms} and standard techniques involving categories of complexes; we omit the proof.
\begin{proposition}
  The pair of subcategories \((\mathcal{C}_m^{\leq 0}, \mathcal{C}_m^{\geq 0})\) forms a bounded \(t\)-structure on \(\mathcal{C}_m\).
\end{proposition}
We call this \(t\)-structure the \defn{standard \(t\)-structure} on \(\mathcal{C}_m\).
Set \(\mathcal{A}_m = \mathcal{C}^{\leq 0}_m \cap \mathcal{C}_m^{\geq 0}\); this is the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, which contains all linear complexes.
It follows that \(\mathcal{A}_m\) is abelian.

@@

\subsection{The Khovanov--Seidel curve model}
In this section we briefly recall how to recover an object of \(\mathcal{C}_{n+1}\) from a wiggly arc on \(n+2\) points on a line.
In fact, the procedure works on more general arcs as well --- namely, those that are not necessarily \(x\)-monotone.
All the results of this section are due to Khovanov and Seidel~\cite{kho.sei:02}.

>>>>

\begin{remark}\label{rem:generating-morphisms}
  It is easy to check that the generating objects \(P_i\) (and hence their graded and homological shifts) satisfy \(\Hom^{0,0}(P_i,P_i) = \Hom^{2,0}(P_i,P_i) = \Hom^{1,0}(P_i,P_{i\pm1}) = k\) and \(\Hom^{g,h}(P_i, P_j) = 0\) in all other cases.
\end{remark}

@@

We refer the reader to e.g.~\cite[Sect.~1.3]{bel.ber.del:82} for the definition of a \(t\)-structure on a triangulated category.
The following proposition is easily checked using the calculations in~\cref{rem:generating-morphisms} and standard techniques involving categories of complexes; we omit the proof.
\begin{proposition}
  The pair of subcategories \((\mathcal{C}_m^{\leq 0}, \mathcal{C}_m^{\geq 0})\) forms a bounded \(t\)-structure on \(\mathcal{C}_m\).
\end{proposition}
We call this \(t\)-structure the \defn{standard \(t\)-structure} on \(\mathcal{C}_m\).
Set \(\mathcal{A}_m = \mathcal{C}^{\leq 0}_m \cap \mathcal{C}_m^{\geq 0}\) to be the heart of this \(t\)-structure; this is the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, which contains all linear complexes.
It follows that \(\mathcal{A}_m\) is abelian.

@@

\subsection{The Khovanov--Seidel curve model}
In this section we briefly recall how to recover an object of \(\mathcal{C}_{n+1}\) from a wiggly arc on \(n+2\) points on a line.
In fact, the procedure works on more general arcs as well --- namely, those that are not necessarily \(x\)-monotone.
